Downstream analysis: A pipeline to analyse time-course gene expression data

### 2019-05-07 scripts/04_downstream_analysis.Rmd
More text, updated stability results, etc
GO term table had disappeared… put it back!

```{r enrichment_analysis, results="hide", message=FALSE}
cluster = 13
genes = gene_names[labels == cluster]

@@

```{r go_to_gene_mapping, results="hide", message=FALSE}
library(topGO)
#source("GO_terms_analysis.R")
genes = biomaRt::getBM(attributes=c("go_id", "refseq_mrna"),
	      values=gene_names,
	      filters="refseq_mrna",
	      mart=ensembl)

@@

>>>>

```{r enrichment_analysis, results="hide", message=FALSE}
cluster = 20
genes = gene_names[labels == cluster]

@@

```{r go_to_gene_mapping, results="hide", message=FALSE}
library(topGO)
genes = biomaRt::getBM(attributes=c("go_id", "refseq_mrna"),
	      values=gene_names,
	      filters="refseq_mrna",
	      mart=ensembl)

@@

go_terms_enriched = go_terms_enriched[
    order(go_terms_enriched[, "resultFisher_padj"]), ]

kable(go_terms_enriched, "html", escape=F, digits=4) %>%
    kable_styling("striped", full_width=TRUE) 
```
